\documentclass[english,bachelor]{swsLeipzig}
%\documentclass[english,master]{swsLeipzig}
% When you change the language, pdflatex may halt on recompilation.
% Just hit enter to continue and recompile again. This should fix it.

\newcommand{\note}[1]{\textcolor{teal}{#1}}

%
% Values
% ------
\ThesisSetTitle{Group Sampling zum Lernen konfigurationsabhängiger Softwareperformance}
\ThesisSetTitleSub{Group Sampling for learning configuration-specific software performance}
\ThesisSetKeywords{} % only for PDF meta attributes

\ThesisSetAuthor{Alexander Zwisler}
\ThesisSetStudentNumber{XXX}
\ThesisSetDateOfBirth{1}{1}{1}
\ThesisSetPlaceOfBirth{XXX}

\ThesisSetSupervisors{XXX,XXX}

\ThesisSetSubmissionDate{11}{2}{2022}
\usepackage{xr} 
\usepackage{nameref}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{placeins}
%
% Suggested Packages 
% ------------------
\usepackage[square, numbers]{natbib}
%   Allows citing in different ways (e.g., only the authors if you use the
%   citation again within a short time).
%
\usepackage{xcolor}
\usepackage{listings}
\usepackage{booktabs}
%    For tables ``looking the right way''.
%
%\usepackage{tabularx}
%    Enables tables with columns that automatically fill the page width.
%
%\usepackage[ruled,algochapter]{algorithm2e}
%    A package for pseudo code algorithms.
%
%\usepackage{amsmath}
%    For tabular-style formatting of mathematical environments.
%
%
% Commenting (by your supervisor)
% ------------------------------- 
\usepackage{xcolor}
\usepackage{soul}
\newcommand{\bscom}[2]{%
% #1 Original text. 
% #2 Replacement text.
\st{\scriptsize\,#1}{\color{blue}\scriptsize\,#2}%
}
\newcommand*{\fullref}[1]{\hyperref[{#1}]{\autoref*{#1} \nameref*{#1}}} % One single link

% Create links in the pdf document
% Hyperref has some incompatibilities with other packages
% Some other packages must be loaded before, some after hyperref
% Additional options to the hyperref package can be provided in the braces []
\usehyperref[hidelinks,backref] % This will add back references in the bibliography
\providecommand{\main}{.} 
\usepackage{graphicx}
\graphicspath{{./resources/} } 
\usepackage{todonotes}
\setlength{\marginparwidth}{3cm}
\usepackage{subfiles}
\setcitestyle{square}


\pagestyle{plain}
\begin{document}
\begin{frontmatter}
  \begin{abstract}
    Modern software systems can often offer many configuration options to adapt the system to
    the needs of the end-user. The influence of configuration options on non-functional
    properties such as performance or energy consumption are often poorly understood.
    Performance influence models help in understanding the influences of configuration
    options on non-functional properties and make it possible to pick optimal configurations
    or find performance hot spots.

    This work introduces an approach to create a performance influence model using an experimental design called "group sampling".
    We apply the group sampling technique to an input space with constraints, which poses a challenge we tackle in this thesis.
    With repeated measurements of the effect different configurations have, we determine the influence
    single configuration options and interactions between them have on a non-functional property.
    We evaluate our performance influence model on real-world datasets and synthetically generated data.
    While the model created proved to be unreliable, the group sampling approach 
    was able to identify influential features with a minimal amount of samples.
     

    \vspace*{\fill}
    \paragraph{}
    Data and code is available at: 
    \begin{itemize}
      \setlength{\itemsep}{1pt}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0pt}
      \item \footnotesize\url{https://git.informatik.uni-leipzig.de/az11kyho/ba-group-sampling}
      \item \footnotesize\url{https://github.com/zwisler-a/bachelor-thesis-group-sampling}
    \end{itemize}    
  \end{abstract}

  \tableofcontents

  
  %\chapter*{Acknowledgements} % optional
  %I thank the authors of the swsLeipzig template for their excellent work!

  \listoffigures % optional

  % \listoftables % optional

  %\listofalgorithms % optional
  %    requires package algorithm2e

  % optional: list of symbols/notation (e.g., using the nomencl package)
\end{frontmatter}

\subfile{chapters/01_introduction.tex}

\subfile{chapters/02_basics.tex}

\subfile{chapters/03_group_sampling.tex}

\subfile{chapters/05_evaluation}

\subfile{chapters/06_discussion.tex}

\subfile{chapters/07_concusion.tex}


% Bibliography
\bibliographystyle{IEEEtranN}
\bibliography{literature}    % load file literature.bib



% \subfile{chapters/appendix.tex}

\end{document}
